The surficial carbon cycle and solid-Earth carbon cycle operate on two different time scales. ~\cite{HRA:2007} considered the short-term carbon budget in the surficial reservoirs: atmosphere, oceans, terrestrial ecosystems and fossil fuels over the time period of years to centuries. The annual transport of carbon due to processes such as weathering, and volcanism are small. However, these processes are dominant on the time scale of millennia. ~\citet{SNH-ZK:2001} constructed a simple carbon reservoir model that spanned from the Archean to present day. Their reservoir model consisted of the following reservoirs: continental sediments, ocean, oceanic crust, and mantle. The following is an overview of carbon in the different reservoirs and their relevant fluxes during the long-term carbon cycle.

Earth's core is considered to contain a large fraction of Earth's carbon inventory. The source of the carbon is attributed to core crystallization and core amalgamation from the giant moon-forming impact. ~\cite{DR-CH-SN:2013} estimates the mass of carbon in the core is $4.44 \times 10^9$ Gt ($1~\text{Gt} = 10^{12}$ Kg). Since the giant moon-forming impact, there is little to no evidence of the exchange of carbon from the core to the mantle. 



~\citet{KHW:1995} estimates $4.2 \times 10^7$ Gt of carbon in the continental crust attributing about 80\% to carbonate sediments. ~\citet{UHC:1952} attributed the source of this carbon as a result of drawdown from the atmosphere due to exposed $\mathrm{Ca}^{2+}$ or $\mathrm{Mg}^{2+}$ silicate bearing rocks undergoing silicate weathering in a reaction known as Urey reaction~\cite{UHC:1952}

\begin{equation}
\label{EQ:Urey_reaction}
  \text{CO}_2 + \text{CaSiO}_3 \rightarrow \text{CaCO}_3 + \text{SiO}_2.
\end{equation}

\noindent The controlling parameters of this reaction are poorly understood but show dependence on the concentration of C, temperature in the atmosphere, sea levels, and rainfall.  

Although the atmosphere presently contains a small fraction of Earth's carbon inventory,~\citet{KJD:2002} suggests that a significant fraction of Earth;s initial carbon inventory resided in the atmosphere which was subsequently drawn down until cooling of global magma ocean and then further drawn down as the continental crust was being built. ~\citet{KHD:2002} estimates that this drawdown before reaching quasi-steady state could of been completed by the end of Archean or 1.5Ga ago at the latest. Alternatively, the atmosphere may have contained only a small fraction of the Earth;s carbon inventory thoughout its history with the Urey reaction as an important controlling process on the flux rate of carbon from the atmosphere to the continental crust. The source of the carbon in this model is associated with the mantle due to a higher flux of carbon release from volcanism in comparison to the flux of carbon subducted.

The oceans are an extremely important reservoir although they contain a relatively insignificant amount of carbon. The byproducts of silicate weathering are transported into the oceans by river systems where organic and inorganic percipitation of carbonates occurs. The resulting pelagic carbonates at the oceanic floor is then subducted or resurfaced as carbon dioxide byproduct of reverse Urey reaction as island arc volcanism. MORB volcanism and hydrothermal vents degass carbon whose source is the mantle. Thus, the ocean plays and important role acting as an intermediary reservoir in the long term carbon cycle.

{\renewcommand{\arraystretch}{2.0}% for the vertical padding
\begin{table}[b!]
    \centering
    \begin{tabular}{|l|l|l|c|c|}
        \hline
        Reservoir & Symbol & Mass of carbon Gt & Reference \\
        \hline
        Core   & $^cM_c$ & $4 \times 10^9$ & ~\citet{DR:2013}  \\
        \hline
        Mantle & $^cM_m$ & $2 \times 10^8$ & ~\citet{KLH-TDL-WM:2017}  \\
        \hline
        Continental crust & $^cM_{cc}$ & $4.2 \times 10^7$ & ~\citet{KHW:1995} \\
        \hline
        Oceans & $^cM_o$ & $3.8 \times 10^4$ & ~\citet{HRA:2007} \\
        \hline
        Atmosphere & $^cM_a$ & $8.5 \times 10^2$ & ~\citet{NOAA:2017} \\
        \hline
        Total & & $4.24 \times 10^9$ & \\
        \hline
    \end{tabular}
    \caption{\doublespacing Masses of carbon in the Earth's carbon reservoirs (1 Gt $= 10^{12}$ kg) ~\cite{KLH-TDL-WM:2017}.
    }
    \label{Table:Masses of carbon in Earth's reservoirs}
\end{table}